The necessity of hypermedia RDF and an approach to achieve it

### 2012-04-12 eswc-2012/workshop2.tex
todo comments
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@213 43ef1190-90fd-4dd7-a769-d0121f02b80e
reformat long lines
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@214 43ef1190-90fd-4dd7-a769-d0121f02b80e
move RaUL again, it is not really what we want
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@215 43ef1190-90fd-4dd7-a769-d0121f02b80e

@@

%As noted in \cite{sunsetonmvc} 
AtomPub has a single service endpoint,
and you can navigate to what you need from there. This motivates the
first discussion topic of this paper:

@@

We noted that for a read-write RESTful protocol, we need to say in the
RDF message itself what kind of operations can be made. We also note
that only information resources can be manipulated, and we argued that
it should be possible to add the required triples to every
resource. We should be able to define hypermedia RDF in terms of a
minimal vocabulary, but like the H~Factor web page, we will find it
instructive to use examples. In the following, we use Turtle syntax,
with prefixes omitted for brevity. Also, we note that in many cases,
we are making statements about the current resource, which given a
reasonable base URI can be written as \texttt{<>}. We have not found
the following factors to be relevant to RDF: \textsf{LE} (embedded
links), \textsf{CR} and \textsf{CU} (control data for read and update
requests respectively); and \textsf{LO} and \textsf{CL} are trivially
supported. The remaining are:

@@

\item[\textsf{LT}] Support for templated queries (HTTP GET)

@@

@@

\begin{verbatim}
<> hm:canBe hm:mergedInto, hm:replaced, hm:deleted ;
   hm:createSimilarAt <../> ;
   hm:acceptsFormats <http://www.w3.org/ns/formats/Turtle> ;
   void:inDataset [ void:sparqlEndpoint </sparql> . ] .
\end{verbatim}

>>>>

% TODO:
% Explain HATEOAS
% More on new H-factors
% References
% POST in relation to graph store
% Weakness of RDF

@@

% TODO: rough start
AtomPub has a single service endpoint, and you can navigate to what
you need from there. This motivates the first discussion topic of this
paper:

@@

We noted that for a read-write RESTful protocol, we need to say in the
RDF message itself what kind of operations can be made. We also note
that only information resources can be manipulated, and we argued that
it should be possible to add the required triples to every
resource. We should be able to define hypermedia RDF in terms of a
minimal vocabulary, but like the H~Factor web page, we will find it
instructive to use examples. In the following, we use Turtle syntax,
with prefixes omitted for brevity. Also, we note that in many cases,
we are making statements about the current resource, which given a
reasonable base URI can be written as \texttt{<>}. We have not found
the following factors to be relevant to RDF: \textsf{LE} (embedded
links), \textsf{CR}, \textsf{CU} (control data for read and update
requests respectively) and \textsf{LT} (templated queries); and
\textsf{LO} and \textsf{CL} are trivially supported. The remaining
are:

@@

@@

\item A factor for RaUL templates.

@@

\begin{verbatim}
<> hm:canBe hm:mergedInto, hm:replaced, hm:deleted ;
   hm:createSimilarAt <../> ;
   hm:acceptsFormat <http://www.w3.org/ns/formats/Turtle> ;
   void:inDataset [ void:sparqlEndpoint </sparql> . ] .
\end{verbatim}
